### 2023-11-09 manuscript/manuscript.Rmd
replace 'tractable' with 'traceable'

For investigators, manual consideration of putative annotations is time-consuming and often difficult to deduce due to the complex interactions between ions and molecules and their mathematical possibilities forming *m/z* features.
It is important that software package implementations can automate this process but also provide tractable results and simple input parameters for easy and wide applicability.

>>>>

For investigators, manual consideration of putative annotations is time-consuming and often difficult to deduce due to the complex interactions between ions and molecules and their mathematical possibilities forming *m/z* features.
It is important that software package implementations can automate this process but also provide traceable results and simple input parameters for easy and wide applicability.
